---
title: "Statistical Inference Course Project Part 2"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

### Muhammad Ali Shaaban  
### 18 December 2018  

## Peer Graded Assignment: Statistical Inference Course Project


```{r setup, include=FALSE}
set.seed(19413)
```

## Instructions  
The project consists of two parts:

 - A simulation exercise.
 - Basic inferential data analysis.
 
# Part 2: Basic Inferential Data Analysis Instructions  

Now in the second portion of the project, we're going to analyze the ToothGrowth data in the R datasets package.  

Load the ToothGrowth data and perform some basic exploratory data analysis

```{r}
library(datasets)
data(ToothGrowth)
library(ggplot2)

str(ToothGrowth)
```

```{r}
head(ToothGrowth)
```

```{r}
summary(ToothGrowth)
```

```{r}
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len, fill=supp)) +
    geom_bar(stat="identity") +
    facet_grid(. ~ supp) +
    xlab("Dose(mg)") +
    ylab("Tooth length")
```

hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

```{r}
hypoth1 <- t.test(len ~ supp, data = ToothGrowth)
hypoth1$conf.int
```

```{r}
hypoth1$p.value
```

```{r}
hypoth2<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 0.5))
hypoth2$conf.int
```

```{r}
hypoth2$p.value
```

```{r}
hypoth3<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 1))
hypoth3$conf.int
```

```{r}
hypoth3$p.value
```

```{r}
hypoth4<-t.test(len ~ supp, data = subset(ToothGrowth, dose == 2))
hypoth4$conf.int
```

```{r}
hypoth4$p.value
```


## Conclusions  

OJ ensures more tooth growth than VC for dosages 0.5 & 1.0. OJ and VC givesthe same amount of tooth growth for dose amount 2.0 mg/day. For the entire trail we cannot conclude OJ is more effective that VC for all scenarios.
